Manuscript Figures

### 2021-08-26 src/manuscript_figures.Rmd
move function from Rmd to utility script with common functions

```{r}
get_top_by_label <- function(dt, label.type, topN = 5) {
  do.call(rbind, lapply(split(dt, dt[,get(label.type)]), function(x) {head(x, topN)}))
}

# find percent contribution of different datatypes to the top factor specific variables 
# LFs: Latent factors; nested list
# FWs: Feature weights for each LF; nested list 
# tool: pca/maui/mofa
# project: e.g. pancancer
# datatype: e.g. cnv_gex_mut
# factors: factor vector (e.g. cancer types for each sample or subtype info for each sample)
# top_lfs: top LF to pick per factor
# top_featuers: top features to pick per latent factor
plot_datatype_contribution_by_factor <- function(LFs, FWs, tool, project, datatype, 
                                                 factors, top_lfs = 1, top_features = 100) {
  experiment <- paste0(project, '.', datatype)
  L <- LFs[[tool]][[experiment]]
  W <- FWs[[tool]][[experiment]]
  dt <- get_factor_specific_variables(L, factors)
  top_vars <- get_top_by_label(dt[padj < 0.05][order(padj)], 'ref_cl', topN = top_lfs)
  # for each factor, pick top lfs and pick top features per lf and plot composition
  freq <- do.call(rbind, lapply(split(top_vars, top_vars$ref_cl), function(x) {
    l <- unique(x$variable) # one or more lfs 
    # get top features per lf and concatenate
    f <- do.call(c, lapply(l, function(y) {
      head(sort(abs(W[,y]), decreasing = T), top_features)
    }))
    freq <- data.table(table(sub("^(.+?)\\..+$", "\\1", unique(names(f)))))
    freq$factor <- unique(x$ref_cl)
    colnames(freq)[1] <- 'omics'
    return(freq)
  }))

  ggplot(freq, aes(x = factor, y = N)) + 
    geom_bar(stat = 'identity', aes(fill = omics), 
             position = 'fill') + coord_flip() + 
    labs(x = '', y = 'Percentage of top features contributing to top latent factors')
}
```

>>>>

```{r}
get_top_by_label <- function(dt, label.type, topN = 5) {
  do.call(rbind, lapply(split(dt, dt[,get(label.type)]), function(x) {head(x, topN)}))
}
```
